%% cv.tex
%
% Author: Dragan Vujović <dvujovic@protonmail.ch>
% URL: https://github.com/draganvu/cv-latex
% License: MIT
%

\documentclass[11pt, a4paper]{article}

% Packages
\usepackage{geometry} % used setting for page margins
\usepackage{hyperref} % used to set hyperlinks and pdf metadata
\usepackage{titlesec} % used to customize sections
\usepackage{setspace} % custom line spacing
\usepackage{enumitem} % needed for item spacing

% Set page margins (assumes A4 paper)
\geometry{
  left=2.5cm,
  top=2.5cm,
  right=2.5cm,
  bottom=2.5cm
}

% Prevent paragraph indentation
\setlength\parindent{0pt}

% Set line spacing
\setstretch{1.0}

% Set item spacing
\setlist[itemize]{itemsep=0em, topsep=0.5em}

% Customize sections
\titleformat{\section}
{\normalfont\Large\bfseries}
{\thesection}{}{}[\titleline{\color{red}\titlerule[.4pt]}]

\newcommand{\myname}{Dragan Vujović}

% Define hyperlink appearance and metadata for pdf properties
\hypersetup{
  pdftitle    = {\myname: Curriculum Vitae},
  pdfauthor   = {\myname},
  pdfkeywords = {Software Engineering, CV, Resume},
  pdfsubject  = {Curriculum Vitae},
  colorlinks  = true,
  urlcolor    = blue,
  citecolor   = magenta,
  linkcolor   = red,
}

\begin{document}

\begin{Huge}
  \myname
\end{Huge}

\medskip Geneva, Switzerland

\vspace{1pt}
\begin{tabular}{@{} l l }
  Phone: & +555 5555 5555\\
  Email: & \href{mailto:dvujovic@protonmail.ch}{dvujovic@protonmail.ch}\\
  Github: & \href{https://github.com/draganvu}{https://github.com/draganvu}\\
  Website: & \href{https://draganvu.github.io/}{https://draganvu.github.io/}
\end{tabular}
  
\section*{Professional Experience}
Software Company Ltd. \hfill Geneva\\
Project Lead \hfill 2016--2019
\begin{itemize}
  \item List entries start with the \verb|\item| command.
  \item Individual entries are indicated with a black dot, a so-called bullet.
  \item The text in the entries may be of any length.
  \item List entries start with the \verb|\item| command.
\end{itemize}
 
Software Company 2 Ltd. \hfill Podgorica\\
Software Engineer \hfill 2014--2016
\begin{itemize}
  \item List entries start with the \verb|\item| command.
  \item Individual entries are indicated with a black dot, a so-called bullet.
  \item The text in the entries may be of any length.
  \item List entries start with the \verb|\item| command.
\end{itemize}

\section*{Education}
University of Montenegro (UCG) \hfill Podgorica\\
Bsc. Computer Science \hfill 2009--2013\\
Coursework: Algorithms, Mathematics, Databases

\section*{Technical Skills}
\begin{tabular}{@{} l l }
  Programming: & Python, Rust, R, SQL (PostgreSQL, mySQL)\\
  Frameworks: & Pandas, NumPy\\
  Tools: & Linux, Docker, Git, \LaTeX
\end{tabular}

\end{document}
